---
title: "Coding Exercises"
author: "Taryn Dowden"
date: "2025-10-23"
output: html_document
---
```{r}
source("source.R")
```
Data
```{r}
data("knz_bison")
```

Create a new column in the bison dataset that calculates the individual’s age at the time of observation.
```{r}
mutate(knz_bison, age = rec_year - animal_yob)
```

Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
weight_filter <- function(a,b){
  bison_wgt_filter <- filter(knz_bison, between(animal_weight, a, b))
  print(bison_wgt_filter)}

```

Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.
```{r}
knz_bison %>%
  ggplot(aes(x=animal_sex, y = animal_weight)) +
  geom_boxplot()
```
```{r}
knz_bison %>%
  levene_test(animal_weight ~ animal_sex)
```
Very small P value indicate variances are not equal
```{r}
knz_bison %>%
  t_test (animal_weight ~ animal_sex, var.equal = FALSE, detailed = TRUE)
```
Very small p value indicates a significant difference in weights between males and females
